`traveltime`: an R package to calculate travel time across a landscape from user-specified locations

### 2025-05-19 README.Rmd
fix typo `trave_time_singapore` in README, paper, and vignette Also update acknowledgements and endmatter order per VeriXiv

```{r}
#| label: calculate-result
#| echo: true
trave_time_singapore <- calculate_travel_time(
  friction_surface = friction_singapore,
  points = stations
)

trave_time_singapore
```

@@

We present the resulting calculated travel times below where (as expected) the travel times are lowest near station exits and progressively higher further away. Note that the results in `trave_time_singapore` include infinite values (`Inf`  above). The islands to the south and north-east are shown as filled cells in the figure above, i.e., they are not masked out by `singapore_shapefile`. But because those islands they are not connected to any cells with a station, the calculated travel time is infinite, and so these cells do not appear in the figure below.

```{r}
#| label: fig-result
#| echo: true
#| fig-cap: "Map of walking travel time in Singapore, in minutes from 
#|   nearest MRT or LRT station."
ggplot() +
  geom_spatraster(
    data = trave_time_singapore
  ) +
  scale_fill_viridis_c(
    option = "A",
    direction = -1,
    na.value = "transparent"
  ) +
  theme_minimal() +
  labs(fill = "Minutes") +
  geom_spatvector(
    data = singapore_shapefile,
    fill = "transparent",
    col = "grey20"
  )
```

>>>>

```{r}
#| label: calculate-result
#| echo: true
travel_time_singapore <- calculate_travel_time(
  friction_surface = friction_singapore,
  points = stations
)

travel_time_singapore
```

@@

We present the resulting calculated travel times below where (as expected) the travel times are lowest near station exits and progressively higher further away. Note that the results in `travel_time_singapore` include infinite values (`Inf`  above). The islands to the south and north-east are shown as filled cells in the figure above, i.e., they are not masked out by `singapore_shapefile`. But because those islands they are not connected to any cells with a station, the calculated travel time is infinite, and so these cells do not appear in the figure below.

```{r}
#| label: fig-result
#| echo: true
#| fig-cap: "Map of walking travel time in Singapore, in minutes from 
#|   nearest MRT or LRT station."
ggplot() +
  geom_spatraster(
    data = travel_time_singapore
  ) +
  scale_fill_viridis_c(
    option = "A",
    direction = -1,
    na.value = "transparent"
  ) +
  theme_minimal() +
  labs(fill = "Minutes") +
  geom_spatvector(
    data = singapore_shapefile,
    fill = "transparent",
    col = "grey20"
  )
```

### 2025-05-19 paper/paper.qmd
add code doi from zenodo to paper
fix typo `trave_time_singapore` in README, paper, and vignette Also update acknowledgements and endmatter order per VeriXiv

```{r}
#| label: calculate-result
trave_time_singapore <- calculate_travel_time(
  friction_surface = friction_singapore,
  points = stations
)

trave_time_singapore
```

We present the resulting calculated travel times in @fig-result where, as expected, the travel times are lowest near station exits (per @fig-data) and progressively higher further away. Note that the results in `trave_time_singapore` include infinite values (`Inf` above). In @fig-data, the islands to the south and north-east are shown as filled cells, but unconnected with the mainland. The raster cells for these islands appear absent in @fig-result. Because they are not connected to any cells with a station, the calculated travel time is infinite, and so these cells do not appear in @fig-result.

```{r}
#| label: fig-result
#| echo: false
#| fig-cap: "Map of walking travel time in Singapore, in minutes from 
#|   nearest MRT or LRT station."
ggplot() +
  geom_spatraster(
    data = trave_time_singapore
  ) +
  scale_fill_viridis_c(
    option = "A",
    direction = -1,
    na.value = "transparent"
  ) +
  theme_minimal() +
  labs(fill = "Minutes") +
  geom_spatvector(
    data = singapore_shapefile,
    fill = "transparent",
    col = "grey20"
  )
```

@@

@@

@@

# Software availability

All software described here is available from R-Universe <https://idem-lab.r-universe.dev/traveltime> and GitHub <https://github.com/idem-lab/traveltime>, and documented at <https://idem-lab.github.io/traveltime/>.

>>>>

```{r}
#| label: calculate-result
travel_time_singapore <- calculate_travel_time(
  friction_surface = friction_singapore,
  points = stations
)

travel_time_singapore
```

We present the resulting calculated travel times in @fig-result where, as expected, the travel times are lowest near station exits (per @fig-data) and progressively higher further away. Note that the results in `travel_time_singapore` include infinite values (`Inf` above). In @fig-data, the islands to the south and north-east are shown as filled cells, but unconnected with the mainland. The raster cells for these islands appear absent in @fig-result. Because they are not connected to any cells with a station, the calculated travel time is infinite, and so these cells do not appear in @fig-result.

```{r}
#| label: fig-result
#| echo: false
#| fig-cap: "Map of walking travel time in Singapore, in minutes from 
#|   nearest MRT or LRT station."
ggplot() +
  geom_spatraster(
    data = travel_time_singapore
  ) +
  scale_fill_viridis_c(
    option = "A",
    direction = -1,
    na.value = "transparent"
  ) +
  theme_minimal() +
  labs(fill = "Minutes") +
  geom_spatvector(
    data = singapore_shapefile,
    fill = "transparent",
    col = "grey20"
  )
```

@@

# Data and Software availability

All software described here is available from R-Universe <https://idem-lab.r-universe.dev/traveltime> and GitHub <https://github.com/idem-lab/traveltime>, and documented at <https://idem-lab.github.io/traveltime/>. Code used in this paper is released via GitHub as [v4](https://github.com/idem-lab/traveltime/releases/tag/v3), and archived on Zenodo under [DOI 10.5281/zenodo.15347016](https://doi.org/10.5281/zenodo.15347016).

@@

# Acknowledgements

An earlier version of this article has been archived on EarthArXiv <https://doi.org/10.31223/X56M74>

@@
